Tabular Constraint Learning

### 2016-05-02 Paper/ECAI/tabular.tex
Rewrote table and group detection

\tias{Reformulate: describe there's an naive approach...}
Tables are detected by detecting rectangular collections of data and attempting to detect and separate headers from the data.
Especially this last step is a complex task on its own  \cite{header} and a sophisticated implementation goes beyond the scope of this paper.
On well formated data, however, the user will not have to specify tables manually.

\tias{Split extensions and group detection, clarify group detection, example (e.g. currency for extensions)}
Our algorithm also attempts to detect groups within tables by partitioning the data into consecutive, type consistent groups, essentially separating textual and numerical data.
We support some extensions such as currencies and percentual data and our approach allows us to omit manual specifications of groups.

A more elaborate implementation could allow group (and table) detection could be done interactively / visually such that a user can select the groups in a spreadsheet or correct automatically generated groups.
From here on we will assume that groups and tables are given.

>>>>

\subsection{Table and group detection}
We chose to implement a naive approach to extract tables as the detection of tables and headers from data is a complex task on its own (\cite{header}) and a sophisticated implementation goes beyond the scope of this paper.
Our approach first detects rectangular collections of data.
It then attempts to identify the header by looking at the type of the first row.
If this row consists only of textual entries, the row is expected to be the header and is removed, if not, the same procedure is applied on the first column.
We suggest to provide tables in general, for well formated data, however, the user will not have to specify tables manually.

Our approach for detecting groups works by partitioning the data of a table into consecutive, type consistent groups, essentially separating textual and numerical data.
The assumption is that often numerical and textual data are not mixed and this approach works well in practice as often groups do not have to be specified manually\footnote{\samuel{Check on benchmark}}.
Unless an explicit orientation (rows or columns) is provided for the table, this approach will attempt to create both row- and column-groups.

So far we have considered textual and numerical (floating point or integer) data.
Our implementation also supports some extensions such as currencies and percentual data, which is considered to be numerical data.
Moreover, percentual data is corrected to the floating point representation (i.e. divided by 100).

A more elaborate implementation could allow group (and table) detection to be done interactively / visually such that a user can select the groups in a spreadsheet or correct automatically generated groups.
From here on we will assume that groups and tables are given.
